Quantifying Infants' Everyday Restrained Experiences in the Home Using Wearable Inertial Sensors

### 2025-11-21 manuscript_restrained_classification validation.qmd
edited declarations

Human annotation results, which were used for model training and validation are publicly shared on OSF (https://osf.io/a698g/overview?view_only=221d1f2bc8d34b5d9838354224d6da8f).

@@

All the processing scripts are also publicly shared on OSF.

>>>>

Sensor data and video recordings are publicly shared on Databrary (Franchak, 2023). Compiled human annotation results are shared on OSF (https://osf.io/a698g/overview?view_only=221d1f2bc8d34b5d9838354224d6da8f).

@@

All processing scripts, including model training and validation analyses, are publicly shared on OSF as well (https://osf.io/a698g/overview?view_only=221d1f2bc8d34b5d9838354224d6da8f).
